---
title: "Development document"
author: "Matt"
date: "27 4 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Development of the data package for Living Norway

This document serves to outline the desired development of the package 

## Typical workflow

```{r workflow diagram, echo=F, warning=F, message=F}
library(DiagrammeR)
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']

      # edge definitions with the node IDs
      tab1 -> tab2 -> tab3 -> tab4 -> tab5->tab6;
      }

      [1]: 'Create folder structure'
      [2]: 'Write minimum metadata'
      [3]: 'Upload scanned pdfs of field & lab notes to data scan folder'
      [4]: 'Upload raw data to raw data folder'
      [5]: 'Data cleaning files stored in to mapped data folder'
      [6]: 'Metadata saved in xml format in the meta_xml folder'
      ")



```

## Create folder structure

### R functions

#### build_folder_structure()

```{r, echo=T}
#build_folder_structure<-function(project_name=project_name){
#  if(dir.exists(project_name)==TRUE) {
#    print("Directory already exists please check the name and retry")
#  } else{
#    dir.create(paste0(getwd(),"/", project_name))
#   dir.create(paste0(getwd(),"/", project_name,"/", "minimum_metadata"))
#     dir.create(paste0(getwd(),"/",project_name,"/", "data"))
#     dir.create(paste0(getwd(),"/", project_name,"/","data", "/", "raw_data"))
#     dir.create(paste0(getwd(),"/", project_name,"/","data", "/", "mapped_data"))
#     dir.create(paste0(getwd(),"/", project_name,"/","data", "/", "scan_data"))
#     dir.create(paste0(getwd(),"/", project_name,"/","scripts"))
#     dir.create(paste0(getwd(),"/", project_name,"/","meta_xml"))
#     dir.create(paste0(getwd(),"/", project_name,"/","dmp"))
#     rmarkdown::draft(paste0(getwd(),"/", project_name,"/", "minimum_metadata", "/"
#                             ,"minimum_metadata.Rmd"),
#                      template="minimum_metadata", package="TheDataPackage", edit=FALSE)
#       }
# 
# }
# 
# build_folder_structure(project_name = "Test")

```

##### Code registration

Objective::To create the folder structure for a biodiversity project. The structure is as follows:

```
├── minimum_metadata.txt (or .md)
├── docs/  -dokumentation (e.g. procedual reports, laboratory protocols)
├── data/ 
|   ├── scan_data/ - analog data in digital format
|   ├── raw_data/ - raw data - born digital or punched from paper forms
|   ├── mapped_data/ - data mapped from raw data 
├── src/ - scripts et al. used for mapping data
├── meta.xml - metadata in EML
├── dmp.xxx - data managment plan

```
Inputs::The name of the project directory 

Outputs:: A set of folders following the desired structure. A minimum metadata template

Enhancements:: 
* Semi-automation of the metadata 
* Automatic reporting of contents of folders once the user has populated them

## Write minimum metadata

Users will be required to fill in the minimum metadata template

### R functions

#### Validate the data package

##### Code registration

Objective:: A function which checks that the metadata has been filled in and that folders contain files of type x.

Inputs:: A project folder

Outputs:: A list of files in each folder, with file type so that the user can confirm for themselves that the data package is complete

Enhancements::


## Upload scanned datasheets

Users will be required to scan and upload datasheets

### R functions

#### Validate the data package
As above

## Upload raw data

Users will be required to upload raw data

### R functions

#### Validate the data package
As above

## Mapped data

Manipulations and changes to raw data will be saved by the user in this folder. 

[Should we add some generic data cleaning tools here or leave it to the user?]

### R functions

#### Validate the data package
As above


## Metadata in XML format

### R functions

#### Convert metadata to XML
Borrow heavily from EML, emld etc. to convert metadata to XML.

##### Code registration

Objective:: To provide convenient wrapper functions for converting data pack to eml/XML format

Inputs:: R data frame or list of lists

Outputs:: An eml file 

Enhancements:: A Shiny App to make eml (make the workflow in a shiny app)





